### 2013-08-26 doc/dissertation/document/chapters/conclusion/conclusion.tex
whiitespace tweaks

With this work, a new foundation for Monte Carlo Synthetic Acceleration
methods has been laid with new theory, algorithms, and numerical
experiments that demonstrate both their potential to make great
contributions to nuclear engineering calculations in the future and
where the research must go in order to achieve this. By advancing
these techniques, we look forward to future work that will enable the
improved design and analysis of nuclear systems.

>>>>

With this work, a new foundation for Monte Carlo Synthetic
Acceleration methods is developed with new theory, algorithms, and
numerical experiments that demonstrate both their potential to make
great contributions to nuclear engineering calculations in the future
and where the research must go in order to achieve this. By advancing
these techniques, we look forward to future work that will enable the
improved design and analysis of nuclear systems.
